---
title: "TidyTrials"
author: "Dennis Valentine"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TidyTrials}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is an example of how to use the TidyTrials package. This package is essentially an XML wrapper to extract and tidy trials from ClinicalTrials.Gov. The package exists because clinical trials have a broad audience but the data is currently inaccessible to researchers who might be unfamiliar with parsing XML files (i.e. statisticians, geneticists  and maybe some computational biologists). 

This package was developed as part of my PhD when I linked a proteomic panel to ClinicalTrials.Gov to identify known or suspected drug targets as part of our target identification campaign. However, the family of functions have grown to extract more variables. 

```{r setup}
library(TidyTrials)
```


```{r, reading-files}
# This reads in one of the example files
example_file <- system.file("extdat", "NCT00160147.xml", package = "TidyTrials")

```

## Extract The Eligibility Criteria
```{r, Eligibility}
Eligibility <- extract_eligibility(trial_path = example_file)
knitr::kable(Eligibility)

```

## Extract The Outcomes
```{r, Outcomes}
Outcomes <- extract_outcome(trial_path = example_file)
knitr::kable(Outcomes)

```

## Extract The Conditions
```{r, Conditions}
Conditions <- extract_conditions(trial_path = example_file)
knitr::kable(Conditions)

```
